JD notes on effects

### 2022-06-21 manuscript/body.tex
Float for marginal effects
Fixing conclusion

\begin{figure}[!h]

@@

The argument and results we present in this paper supports a greater need for a shift on focus on what and how to present predictions from generalized models. For example, the effect-styled confidence intervals could provide more clarity concerning the uncertainty due to the input variable of interests as opposed to the conventional way of incorporating everything.

>>>>

@@

The argument and results we present in this paper support a greater need for a shift on focus on how to present predictions from generalized models. For example, the effect-styled confidence intervals could provide more clarity concerning the uncertainty due to the input variable of interests as opposed to the conventional way of incorporating everything.
